\begin{thebibliography}{}
		\bibitem{LRP_DNN} Layer-wise Relevance Propagation for Deep
		Neural Network Architectures. Alexander Binder, Sebastian Bach, Gregoire Montavon, Klaus-Robert Müller und Wojciech Samek
		
		\bibitem{CH}Finding and Removing Clever Hans:
		Using Explanation Methods to Debug and Improve Deep Models
		
		\bibitem{dtd_paper} Explaining nonlinear classification decisions with deep Taylor
		decomposition
		
		\bibitem{LRP_first_paper} On Pixel-Wise Explanations for Non-Linear
		Classifier Decisions by Layer-Wise Relevance
		Propagation
		
		\bibitem{TD} S. Bazen, X. Joutard, The Taylor decomposition: a unified generalization of the
		Oaxaca method to nonlinear models, Technical Report 2013-32, Aix-Marseille
		University, 2013.
		
		\bibitem{oaxaca} R. Oaxaca, Male-female wage differentials in urban labor markets, Int. Econ. Rev.
		14 (3) (1973) 693–709
		
		\bibitem{badnets} BadNets: Identifying Vulnerabilities in the Machine Learning Model Supply Chain
		
		\bibitem{XAI:book}Montavon G., Binder A., Lapuschkin S., Samek W., Müller KR. (2019) Layer-Wise Relevance Propagation: An Overview. In: Samek W., Montavon G., Vedaldi A., Hansen L., Müller KR. (eds) Explainable AI: Interpreting, Explaining and Visualizing Deep Learning. Lecture Notes in Computer Science, vol 11700. Springer, Cham. https://doi.org/10.1007/978-3-030-28954-6\_10
		
		\bibitem{lrp_overview} Layer-Wise Relevance Propagation:
		An Overview
		Grégoire Montavon 1 , Alexander Binder 2 , Sebastian Lapuschkin 3 , Wojciech
		Samek 3 , and Klaus-Robert Müller 1,4,5
		
		\bibitem{goingdeeperwithconvolutions}
		Going deeper with convolutions. Christian Szegedy, Wei Liu, Yangqing Jia, Pierre Sermanet, Scott Reed, Dragomir Anguelov, Dumitru Erhan, Vincent Vanhoucke Andrew Rabinovich.\\
		\url{https://arxiv.org/pdf/1409.4842v1.pdf}
		
		\bibitem{twdata}
		Bharath Raj.\\
		\url{https://towardsdatascience.com/a-simple-guide-to-the-versions-of-the-inception-network-7fc52b863202}\\
		zugegriffen am 29.04.2021
		
		\bibitem{vgg16_neurohive}
		Neurohive: VGG16 – Convolutional Network for Classification and Detection. 20 November 2018\\
		\url{https://neurohive.io/en/popular-networks/vgg16/}\\
		zugegriffen am 29.04.2021
		
		\bibitem{vgg16_architecture}
		Understanding the VGG19 Architecture. Aakash Kaushik.\\
		SRM Institute of Science and Technology.\\
		\url{https://iq.opengenus.org/vgg19-architecture/}
		
		\bibitem{optimaltransport_twds}
		Optimal transport: a hidden gem that empowers today’s machine learning. Ievgen Redko. Hubert Curien laboratory UMR CNRS 5516, University Jean Monnet of Saint-Etienne. 15 June 2020.\\
		\url{https://towardsdatascience.com/optimal-transport-a-hidden-gem-that-empowers-todays-machine-learning-2609bbf67e59}\\
		zugegriffen am 29.04.2021
		
		\bibitem{cnn_stanford}
		\url{https://cs231n.github.io/convolutional-networks/}\\
		zugegriffen am 30.04.2021
		
		\bibitem{cnn_architectures_stanford}
		CNN Architectures - Lecture 9. Fei-Fei Li, Justin Johnson, Serena Yeung
		\url{https://www.youtube.com/watch?v=DAOcjicFr1Y}\\
		zugegriffen am 30 April 2021
		
		\bibitem{lrp_alzheimer}
		Moritz Böhle, Fabian Eitel, Martin Weygandt, Kerstin Ritter. Tue, 27 Aug 2019.
		Layer-Wise Relevance Propagation for Explaining Deep Neural Network Decisions in MRI-Based Alzheimer's Disease Classification
		\url{https://arxiv.org/abs/1903.07317}
		
		\bibitem{BatchNormalization}
		Batch Normalization: Accelerating Deep Network Training by Reducing Internal Covariate Shift. 2 März 2015. Sergey Ioffe Christian Szegedy.
		\url{https://arxiv.org/pdf/1502.03167.pdf}
		
		\bibitem{unmasking clever hans} Lapuschkin, S., Wäldchen, S., Binder, A. et al. Unmasking Clever Hans predictors and assessing what machines really learn. Nat Commun 10, 1096 (2019). https://doi.org/10.1038/s41467-019-08987-4
		
		\bibitem{imagenet_unhansed_v1} Analyzing ImageNet with Spectral Relevance Analysis: Towards ImageNet un-Hans'ed.\\
		Christopher J. Anders, Talmaj Marinč, David Neumann, Wojciech Samek, Klaus-Robert Müller, Sebastian Lapuschkin\\
		\url{https://arxiv.org/abs/1912.11425v1}
		
		\bibitem{best_practice_lrp}arXiv:1910.09840v3  [cs.LG]  13 Jul 2020Towards Best Practice in Explaining NeuralNetwork Decisions with LRPMaximilian Kohlbrenner, Alexander Bauer, Shinichi Nakajima, Alexander Binder,Wojciech Samek and Sebastian Lapuschkin
		
		\bibitem{spectralClustering_tut} A Tutorial on Spectral Clustering
		Ulrike von Luxburg
		Max Planck Institute for Biological Cybernetics
		Spemannstr. 38, 72076 Tübingen, Germany
				
	\end{thebibliography}
